---
title: "Who were the winners?"
author: "Tom Gibbens-Matsuyama"
format: html
editor: visual
---

#### Problem:
At the conclusion of the ASDN project the PIs decided to hand out first, second, and third prizes to the observers who measured the most eggs. Who won? Please use R and dbplyr to answer this question, and please submit your R code. Your code should print out:

#### Load libraries
```{r}
library(DBI) 
library(tidyverse)
library(duckdb)
library(dbplyr)
```

#### Connect to the database
```{r}
# Connect to database
conn <- DBI::dbConnect(duckdb::duckdb(), dbdir='database/database.db')

# List tables 
DBI::dbListTables(conn)

# Read in specific tables
egg_table <- tbl(conn, 'Bird_eggs')
personnel <- tbl(conn, "Personnel")
bird_nests <- tbl(conn, "Bird_nests")

```

```{r}

# Calculate total eggs per observer
total_eggs <- inner_join(egg_table, bird_nests, by = "Nest_ID") %>% 
  inner_join(personnel, by = c("Observer" = "Abbreviation")) %>% 
  group_by(Name) %>% 
  summarize(total_eggs = count(Egg_num)) %>% 
  slice_max(order_by = total_eggs, n = 3) %>% 
  arrange(desc(total_eggs))
```

#### Show Query
```{r}
# Query of the code above
inner_join(egg_table, bird_nests, by = "Nest_ID") %>% 
  inner_join(personnel, by = c("Observer" = "Abbreviation")) %>% 
  group_by(Name) %>% 
  summarize(total_eggs = count(Egg_num)) %>% 
  arrange(desc(total_eggs)) %>% 
  show_query()
```
I did not have multiple R statements, therefore I did not create any temporary tables. It was all in one input. 
